### 2016-05-29 README.Rmd
minor updates. see news.md

There are currently two main commands: `vis_dat` and `vis_miss`.

@@

- **new!!** `vis_guess` has a guess at what the value of each cell. So "10.1" will return "double", and `10.1` will return "double", and 01/01/01 will return "date". Keep in mind that it is a **guess** at what each cell is, so you can't trust this fully. `vis_guess` is made possible thanks to Hadley Wickham's `readr` package - thanks mate!

@@

# Example

@@

@@

@@

@@

**Allowing for missings to be visualised/seen when there is a small proportion**

This problem will be approached by adding in a bar at the top of the visualisation that indicates whether there are any missings in a column. I will also add into the legend the % of overall missing/absent.

@@

# Thank you

>>>>

There are currently three main commands: `vis_dat`, `vis_miss`, and `vis_guess`

@@

-  `vis_guess` has a guess at what the value of each cell. So "10.1" will return "double", and `10.1` will return "double", and `01/01/01` will return "date". Keep in mind that it is a **guess** at what each cell is, so you can't trust this fully. `vis_guess` is made possible thanks to Hadley Wickham's `readr` package - thanks mate!

@@

# Examples

## Using `vis_dat`

@@

## using `vis_miss`

@@

The percentages of missing/complete in `vis_miss` are accurate to 1 decimal place.

@@

When there is <0.1% of missingness, `vis_miss` indicates that there is >1% missingness.

test_miss_df <- data.frame(x1 = 1:10000,
                           x2 = rep("A", 10000),
                           x3 = c(rep(1L, 9999), NA))

vis_miss(test_miss_df)

`vis_miss` will also indicate when there is no missing data at all

vis_miss(mtcars)

## using `vis_guess`

@@

@@

# Thank yous
